---
title: "A3: Incarceration"
output: html_document
---

### Introduction

**Nowadays, the disparities about racial demographics in prisons is one of the societal concerns in United States. And it's important to solve this issue. In order to have a clearer understanding to the situation of incarceration, I will use this report to analyze the data and represent them in visualized forms.The chosen variables are year, black_prison_pop.**

### Summary Information

- What is the average value of my variable across all the counties (in the current year)?
  **According to the table generated, all the average values are shown**
  
- Where is my variable the highest?
  **According to the data calculated, it's New York County with a value of 24818**
  
- How much has black_prison_pop change over the last 5 years?
  **According to the data calculated, the black_prison_pop increases 131 over the last 5 years**
  
- How much has black_female_prison_pop change over the last 5 years?
  **According to the data calculated, the black_female_prison_pop increases 10 over the last 5 years**
  
- How much has black_male_prison_pop change over the last 5 years?
  **According to the data calculated, the black_male_prison_pop increases  over the last 5 years**

**I got five values through analyzing the variable of black_prison_pop.For the first information, all the values are shown table. Second value is the county that has the highest black_prison_pop, which is New York County with a value of 24818. The third value is black_prison_pop change over the last 5 years, increasing 131.The fourth and fifth values each find the changes of female and male prison pop, which are 10 and 131**

```{r}
data <- read.csv("https://raw.githubusercontent.com/melaniewalsh/Neat-Datasets/main/us-prison-pop.csv")

```


### The Dataset

```{r}
rows <- nrow(data)
print(rows)
columns <- ncol(data)
print(columns)
```

**The Vera Institute collected data and the data was collected by working with governments , local organizations and community members.The reason for collecting the data is that to stop the incarceration of people of color and people experiencing poverty.There are 153811 observations in the data and 36 features in data.When working with this data, there is an ethical question that is there biased results generated because of the data inaccuracy and missing. Also, there are two limitations with this data. Firstly, the accuracy of specific data is concerning.There might be some data that is not included in data set.Secondly, the data set contains many NAs which will largely affect the result of analyzing, leading to a biased conclusion.**


### Trends Over Time Chart

``````{r, echo = FALSE, code = readLines("chart1_example.R")}
source("chart1_example.R")
trend_chart
```
**The reason I included this chart is to see the trending of the prison population growth over time,having a clearer understanding to the tendency.The chart shows that the Black prison population is larger than the White prison population.Also, the overall prison population is increasing through years.**


### Variable Comparison Chart

```{r}
source("chart2_example.R")
comparison
```

**The reason I included this chart is to have a direct understanding of the comparison of male and female prison population in different counties in WA.From the chart, we can see that the black prison population is are all about male. And the King County has the biggest population**

### Map

```{r}
source("map_example.R")
prison_pop_map
```

**The reason included this map is to have a clear understanding of the black prison population situation in different states in United States. From the map, we can find that in Seattle and some regions in the middle and the north of the United States, the black prison population situation is most serious, about 4K. For most of other states, the color is grey, meaning the black prison population is relatively low.**

